Ms. 2: Consumption and resistance across states and HRRs

### 2017-04-05 states/resistance/ms2.Rmd
ms2 initial

---
title: "Consumption and resistance across states and HRRs"
bibliography: refs.bib
output:
  html_document:
    fig_height: 4
  pdf_document:
    fig_height: 3
---

@@

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, cache=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(broom)
library(pander)
library(assertr)
```

```{r setup}
# swo> I removed Klebsiella because it's mostly in immune-compromised people
# and K. oxytoca because it's from neonatal septicemia?
gram_negs = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

```{r load_data}
hrr = read_tsv('../../../db/hrr/hrr_2011.tsv') %>%
  select(zipcode, hrr)

@@

```{r load_consumption_data}
bene = read_tsv('../../bene_2011.tsv') %>%
  left_join(hrr, by='zipcode')
pde = read_tsv('../../pde_2011.tsv') %>%
  select(bene_id, drug=antibiotic) %>%
  left_join(select(bene, bene_id, state, hrr), by='bene_id')

na20 = function(x) if_else(is.na(x), 0L, x)

state_denom = bene %>% count(state) %>% rename(n_bene=n)
state_consumption = pde %>%
  group_by(state, drug) %>%
  summarize(n_claims=n()) %>%
  ungroup() %>%
  left_join(state_denom, by='state')

hrr_denom = bene %>% count(hrr) %>% rename(n_bene=n)
hrr_consumption = pde %>%
  group_by(hrr, drug) %>%
  summarize(n_claims=n()) %>%
  ungroup() %>%
  left_join(hrr_denom, by='hrr')

# State-level consumption data
#state_consumption = read_tsv('../bene-consumption/state_usage_2011.tsv') %>%
  #filter(!is.na(state)) %>%
  #right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  #group_by(state, drug_group) %>%
  #summarize_at(vars(cpkp, did), sum)

hrr_consumption = read_tsv('../bene-consumption/hrr_usage_2011.tsv') %>%
  filter(!is.na(hrr)) %>%
  right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  group_by(hrr, drug_group) %>%
  summarize_at(vars(cpkp, did), sum)

state_dat = left_join(abg, state_consumption, by=c('drug_group', 'state'))
hrr_dat = left_join(abg, hrr_consumption, by=c('drug_group', 'hrr'))
```

```{r run_models}
safe_spearman = function(df, expl, indep) {
  try(return(cor.test(df[[indep]], df[[expl]], method='spearman') %>% tidy), silent=TRUE)
  data_frame(estimate=NA, statistic=NA, p.value=NA, method=NA, alternative=NA)
}

models = function(df, indep, keep=NULL) {
  lapply(c('cpkp', 'did'), function(expl) {
    safe_spearman(df, expl, indep) %>%
      mutate(explanatory=expl)
  }) %>% bind_rows
}

pvalue_stars = function(x) {
  case_when(x < 0.001 ~ '***',
            x < 0.01 ~ '**',
            x < 0.05 ~ '*',
            x < 0.1 ~ 'o',
            TRUE ~ '')
}

>>>>

---
title: "Ms. 2: Consumption and resistance across states and HRRs"
bibliography: refs.bib
output:
  html_document:
    fig_height: 4
  pdf_document:
    fig_height: 3
---

@@

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, cache=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
import::from(broom, tidy)
library(pander)
library(assertr)
```

```{r setup}
gram_negs = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

```{r load_data}
hrr = read_tsv('../../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr)

@@

```{r load_consumption_data}
state_usage = read_tsv('../bene-consumption/state_usage.tsv') %>%
  filter(year==2011) %>%
  right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  group_by(hrr, drug_group) %>%
  summarize_at(vars(cpkp, did), sum)

hrr_usage = read_tsv('../bene-consumption/hrr_usage.tsv') %>%
  filter(year==2011) %>%
  right_join(consumption_groups, by=c('antibiotic'='drug')) %>%
  group_by(hrr, drug_group) %>%
  summarize_at(vars(cpkp, did), sum)

state_dat = left_join(abg, state_usage, by=c('drug_group', 'state'))
hrr_dat = left_join(abg, hrr_usage, by=c('drug_group', 'hrr'))
```

```{r run_models}
pvalue_stars = function(x) {
  case_when(x < 0.001 ~ '***',
            x < 0.01 ~ '**',
            x < 0.05 ~ '*',
            x < 0.1 ~ 'o',
            TRUE ~ '')
}
